The Evolution of Phenotypically Invariant Genetic Networks

### 2017-11-29 kalman_walk_paper.tex
plots

>>>>

  \begin{figure}[H]
    \centering
    \begin{tabular}{ccc}
      \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{examples/osc_F1_hundreth_tau0} &
      \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{examples/osc_F2_hundrethtau0} \\
      \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{examples/osc_F1_tenth_tau0.pdf} &
      \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{examples/osc_F2_tenthtau0.pdf} \\
      \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{examples/osc_F1_half_tau0.pdf} &
      \includegraphics[width=0.5\textwidth, height=0.125\paperheight]{examples/osc_F2_halftau0.pdf}
    \end{tabular}
    \end{figure}
